Gromov--Witten theory of hypersurfaces in genus one

### 2019-03-01 GenusOneRelativeMaps.tex
finished step 4, except for triviality of Psi_b when no negative markings

The base for the induction is the case of a single relative marking $x_1$ with full tangency $\alpha_1=d$. Write the insertion as $\gamma=\tau_{b_1}(\gamma_1)\tau(\gamma)_{\geq 2}$. We shall add a non-relative marking $x_0$ and, starting from the equality $c_1(L_{0,\rm{not\ bot}})\cdot[\VZ_{1,\alpha}(P|H_0+H_\infty)^\sim]=\ldots$ (the boundary classes described above), intersect it with $\bar\gamma=\fgt_{x_1}^*\left(\psi_0^{b_1}\ev_0^*(\gamma_1)\tau(\gamma)_{\geq 2}\right)$. \begin{comment}{$\bar\gamma=\fgt_{x_1}^*\left(\psi_0^{b_1}\ev_0^*(\gamma_1)\tau(\gamma)_{\geq 2}\right)$\end{comment}
On the right-hand side, all the not recursively known terms consist of an elliptic curve of degree $d$ in the bottom level, and a rational tail of horizontal degree $0$ in the top level. The rational tail supports $x_0$ by assumption, and it must support $x_1$ as well by balancing: if any other marking is on it, the invariant is recursively known (lower $n$); otherwise, we recover the invariant we are trying to compute (up to corrections from comparing $\psi_k$ and $\fgt_{x_1}^*\psi_k$, which again involve invariants with lower $n$). On the left hand side, write $c_1(L_{0,\rm{not\ bot}})=\Psi_b-\ev_0^*H=-\ev_0^*H$ by \ref{claim:trivialPsib} above. We can therefore compute the left-hand side by forgetting $x_1$ and the \emph{first reduction}: the result is the absolute invariant $-d^2\langle\tau_{b_1}(H\cdot\gamma_1)\tau(\gamma)_{\geq2}\rangle^{H,\rm{red}}_{1,n,d}$, which is recursively known.
\newpage

>>>>

The base for the induction is the case of a single relative marking $x_1$ with full tangency $\alpha_1=d$. Write the insertion as $\gamma=\tau_{b_1}(\gamma_1)\tau(\gamma)_{\geq 2}$. We shall add a non-relative marking $x_0$ and, starting from the equality $c_1(L_{0,\rm{not\ bot}})\cdot[\VZ_{1,(0)\cup\alpha}(P|H_0+H_\infty)^\sim]=\ldots$ (the boundary classes described above), intersect it with $\bar\gamma=\fgt_{x_1}^*\left(\psi_0^{b_1}\ev_0^*(\gamma_1)\tau(\gamma)_{\geq 2}\right)$.
On the right-hand side, all the not recursively known terms consist of an elliptic curve of degree $d$ in the bottom level, and a rational tail of horizontal degree $0$ in the top level. The rational tail supports $x_0$ by assumption, and it must support $x_1$ as well by balancing: if any other marking is on it, the invariant is recursively known (lower $n$); otherwise, we recover the invariant we are trying to compute (up to corrections from comparing $\psi_k$ and $\fgt_{x_1}^*\psi_k$, which again involve invariants with lower $n$). On the left hand side, write $c_1(L_{0,\rm{not\ bot}})=\Psi_b-\ev_0^*H=-\ev_0^*H$ by \ref{claim:trivialPsib} above. We can therefore compute the left-hand side by forgetting $x_1$ and the \emph{first reduction}: the result is the absolute invariant $-d^2\langle\tau_{b_1}(H\cdot\gamma_1)\tau(\gamma)_{\geq2}\rangle^{H,\rm{red}}_{1,n,d}$, which is recursively known.

The general induction step is similar: say $x_1$ is a positive marking. Introduce a non-relative marking $x_0$ and, starting from the equality $c_1(L_{0,\rm{not\ bot}})\cdot[\VZ_{1,(0)\cup\alpha}(P|H_0+H_\infty)^\sim]=\ldots$ (the boundary classes described above), intersect it with $\bar\gamma=\fgt_{x_1}^*\left(\psi_0^{b_1}\ev_0^*(\gamma_1)\tau(\gamma)_{\geq 2}\right)$. On the right hand side, the interesting terms have a $(g,d)$ splitting equal to $\{(1,d),(0,0)\}$, and the top component contains $x_0$. If the rational tail is top: either it contains only $x_0$ and $x_1$, and we recover the invariant we want to compute (up to correction terms with less than $n$ markings); or it contains $x_0$ and another positive marking, in which case the genus one invariant can be computed by $\fgt_{x_1}$ and the first reduction; or it contains more than two markings, which leaves less than $n$ on the genus one component. On the other hand, if genus one is top: either it contains $x_1$ and can therefore be computed by forgetting it; or it doesn't, but then the bottom component needs to support at least a negative marking, so the genus one component contains less than $n^\prime$ relative markings.

We shall now address the left-hand side: assume there is a negative marking $x_2$ (if not, $\Psi_b$ is trivial and we conclude as above). Write $c_1(L_{0,\rm{not\ bot}})=\Psi_b+\ev_0^*H=-\alpha_2\hat\psi_2-\ev_2^*H+\ev_0^*H=-\alpha_2\fgt_{x_1}^*\psi_2-\ev_2^*H+\ev_0^*H-\alpha_2(\delta_{2,\rm{triv}}+\delta_{1,2})$. The issue is to control the latter terms. Let us start from $\delta_{2,\rm{triv}}$: the curve splits into a bottom and a top component ($C_b$ and $C_t$), with $x_2$ attached to $C_t$. As usual we are interested in the case that there is a component of genus one and degree $d$. If $C_b$ is rational, it must contain at least two markings, one of which is negative: either it contains $x_1$ as well (then $C_t$ has less than $n^\prime$ relative markings), or it doesn't (then the top invariant can be computed by $\fgt_{x_1}$). If $C_t$ is rational, the argument is symmetric. Finally, the invariants from $\delta_{1,2}$ can again be computed by induction on $n^\prime$. This concludes the inductive procedure.
\newpage
